Understanding data fabrication: Qualitative Comparative Analysis (QCA) of

### 2018-03-27 submission/redraft.rmd
Add paragraph

We conducted three separate csQCA analyses combining the coded data fabrication characteristics with the outcomes of these statistical detection methods. 
In csQCA, unique combinations with conflicting outcomes are either omitted (similar to listwise deletion) or additional characteristics are inductively added to resolve the conflicting outcomes [@rihoux2008]. 
Here, we omit conflicting outcomes for analysis and try to qualitatively assess potentially relevant characteristics. 
We do not run new QCAs because adding additional characteristics quickly increases the state space of unique patterns to 128 (by just adding two) or beyond (512 by adding four). 
If we would add two characteristics it  would result in maximum coverage of `r round((28/128) * 100, 0)`%; maximum coverage would be `r round((28/512) * 100, 0)`% if we add four characteristics.

We used the R package `QCA` [@;@] to conduct these csQCAs. 
For each of the three statistical methods to detect data fabrication, we assessed both sufficient and necessary conditions for detection as well as going undetected. 
We minimized the truth tables using the enhanced Quine-McCluskey algorithm [@]. 
Data are available at [osf.io/xxxxx](https://osf.io/xxxxx); analysis code is available at [osf.io/xxxxx](https://osf.io/xxxxx).

<!-- As such, we minimized the truth tables with the outcome measuresfor both detecting data as fabricated and for fabricated data going undetected. 
As such, we initially conduct ten QCA's, with at most ten more in the case of conflicting outcomes in for all methods. -->
<!-- https://raw.githubusercontent.com/chartgerink/2015ori-2/c706d77e4d85daa285624028d379d7b9b00bd1d0/submission/manuscript.Rmd -->
<!-- 
# Results

@@

# Discussion -->

>>>>

We conducted separate csQCA analyses combining the coded data fabrication characteristics with the outcomes of these statistical detection methods. 
Usually, unique combinations in csQCA with conflicting outcomes are either omitted (comparable to listwise deletion) or additional characteristics are inductively added to resolve the conflicting outcomes [@rihoux2008]. 
Here, we omit conflicting outcomes for analysis and try to qualitatively assess potentially relevant characteristics. 
We do not run additional QCAs because adding additional characteristics quickly increases the state space of unique patterns to 128 (by just adding two) or beyond (512 by adding four). 
If we would add two characteristics it  would result in maximum coverage of `r round((28/128) * 100, 0)`% by our participants; maximum coverage would be `r round((28/512) * 100, 0)`% if we add four characteristics.

We used the R package `QCA` [@r-core;@10.1016/j.jbusres.2007.01.002] to conduct these csQCAs. 
For each of the three statistical methods to detect data fabrication, we assessed both sufficient and necessary conditions for detection as well as going undetected. 
We minimized the truth tables using the enhanced Quine-McCluskey algorithm [@10.1002/j.1538-7305.1956.tb03835.x]. 
Data are available at [osf.io/xxxxx](https://osf.io/xxxxx); analysis code is available at [osf.io/xxxxx](https://osf.io/xxxxx).

<!-- https://raw.githubusercontent.com/chartgerink/2015ori-2/c706d77e4d85daa285624028d379d7b9b00bd1d0/submission/manuscript.Rmd -->

# Results

@@

For each participant, we provide a qualitative summary of the interview with selected quotes. 
These summaries can be read separately from each other and provide detailed descriptions of our participants' fabrication process. 
We share these summaries here and not in an appendix because this paper focuses on a qualitative evaluation of the data fabrication strategies applied. 
In Table xxxx we present an overview of the participant characteristics with hyperlinks to the raw transcript files [@10.5281/zenodo.832491] and to the summaries provided in this manuscript (only available in the HTML version of this manuscript).

| ID |  
| -- |

<!-- Insert table with participant characteristics here -->

### Participant 0jg

## csQCA

```{r}

```

<!-- # Discussion -->
